Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-07-22 text/manuscript-full-KS.qmd
update rq2 data sentence

In particular, we answer the second research question by analyzing particular student list purchases that did *not* utilize the Geomarket search filter and purchased prospects from all Geomarkets in a particular metropolitan area.[^19] For each prospect, we know their home zip code and, therefore, which Geomarket they belong to. Our analyses then show which students would have been included or excluded from the student list purchase had the purchase filtered on particular Geomarkets.

>>>>

In particular, we answer the second research question by analyzing particular student list purchases that did *not* utilize the Geomarket search filter and purchased prospects from all Geomarkets in a particular metropolitan area.[^19] For each prospect, we know their high school, and the exact longitude and latitude of their high school, which we use to assign high school students to Geomarkets. Our analyses then show which students would have been included or excluded from the student list purchase had the purchase filtered on particular Geomarkets.
